Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2021-11-02 PrevAdjSurvey.tex
Updates from Overleaf

We also apply these two methods to a real data set from \cite{Kali:2021}.
This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = "252\%\)).
The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.56\%, "7.54\%).

@@

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_lower_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:perfect_upper_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_lower_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_50_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_50_0_05_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_005_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_8000_0_005_reduced}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
    \caption{Caption}
    \label{fig:imperfect_upper_error_frequency_8000_0_05_reduced.pdf}
\end{figure}

>>>>

We also apply these two methods to a real data set from \cite{Kali:2021}.
This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = 252\%\)).
The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.56\%, "7.54\%).

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_coverage_50_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:imperfect_coverage_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_coverage_50_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:imperfect_coverage_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:imperfect_coverage_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_coverage_8000_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:imperfect_coverage_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:imperfect_lower_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_50_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:imperfect_lower_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:imperfect_lower_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:imperfect_lower_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:imperfect_upper_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_50_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:imperfect_upper_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:imperfect_upper_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/imperfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:imperfect_upper_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_coverage_50_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:perfect_coverage_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_coverage_50_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:perfect_coverage_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_coverage_8000_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:perfect_coverage_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_coverage_8000_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:perfect_coverage_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:perfect_lower_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_50_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:perfect_lower_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:perfect_lower_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_lower_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:perfect_lower_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:perfect_upper_error_frequency_50_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_50_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:perfect_upper_error_frequency_50_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_005_prev.pdf}
\caption{Caption}
\label{fig:perfect_upper_error_frequency_8000_groups_0_005_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/perfect_upper_error_frequency_8000_groups_0_05_prev.pdf}
\caption{Caption}
\label{fig:perfect_upper_error_frequency_8000_groups_0_05_prev}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/simple_coverage_comparison_plot.pdf}
\caption{Caption}
\label{fig:simple_coverage_comparison_plot}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/simple_coverage_error_comparison_plot.pdf}
\caption{Caption}
\label{fig:simple_coverage_error_comparison_plot}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/simple_lower_error_frequency_comparison_plot.pdf}
\caption{Caption}
\label{fig:simple_lower_error_frequency_comparison_plot}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=\textwidth]{figures/simple_upper_error_frequency_comparison_plot.pdf}
\caption{Caption}
\label{fig:simple_upper_error_frequency_comparison_plot}
\end{figure}
